---
title: "Who are the elected representatives?"
output:
  html_document: default
css: styles.css
---


This is the stub of the .rmd file you should use to create you
representatives' overview.  Please fill in the missing part, write the
code, and delete the instructions.


```{r setup, include=FALSE}
## this is the code chunk for R setup.
## You may load libraries and your google key here
## You can also set various knitr options here
knitr::opts_chunk$set(echo=FALSE, message=FALSE)
library(dplyr)
source("~/Documents/keys.R")
source('process-data.R')
```

Set the addresses in a code chunk.  These are the addresses the user
can modify
```{r}
address1 <- "puyallup, WA"
                           # imprecise addresses may (or may not) work
address2 <- "2199 S University Blvd, Denver, CO 80208"
                           # good if you have correct street address
```

# Elected officials for the first address

Write a few words and print the address in an inline code chunk

```{r}
tbl <- repTable(address1)
## You may also want to do some additional processing here
## Obviosly, you may pick different function and variable name.
## You may want to consider knitr::kable for improved table printing, look
## for details at the rmarkdown page at
## http://rmarkdown.rstudio.com/index.html
knit::kable(tbl)
```

# Elected officials for the second address

This section should be very similar to the previous section: write a
few words and print the address in an inline code chunk

```{r}
tbl <- repTable(address2)
knit::kable(tbl)
```

